### 2013-12-15 GIS/Project/Documentation/report2/report2.tex
Finished 'Example' section

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[MeX]{polski}
\usepackage{tikz}

\title{Grafy i Sieci. Sprawozdanie 2. \\ \small{SK11 Kolorowanie grafu za pomocą przeszukiwania z tabu.}}
\author{Michał Aniserowicz, Jakub Turek}
\date{}

\begin{document}

\maketitle

\section{Temat projektu}

SK11 Kolorowanie grafu za pomocą przeszukiwania z tabu.

\input{report2_algorithm.tex}
\input{report2_data_structures.tex}
\input{report2_testing.tex}
\input{report2_program_principles.tex}
\input{report2_example.tex}

\end{document}