### 2014-01-07 PTKB/DSA/Documentation/documentation.tex
Introduced documentation stub

\documentclass{article}
\usepackage[MeX]{polski}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}

\title{Dokumentacja końcowa projektu \\ \Large{Algorytm DSA}}
\author{Jakub Turek}
\date{}

\begin{document}

    \maketitle

    \section*{Section stub}

    Sentence stub.

\end{document}